Open Preprints in Ecology \& Evolution

### 2012-09-04 ms.tex

Preprints servers such as arXiv are common in mathematics and physics, but still
a minority of papers in ecology and evolution use them. Preprints servers allow
author to make their manuscripts publicly available before submitting them to
journals for peer-review. ... The idea became popular with arXiv, and many
physicists start their day with a look at the new papers in arXiv \cite{gin11}

@@

\begin{figure}[ht!] \centering\includegraphics[width=0.50\textwidth]{map.pdf}
\caption { It can take several months, and even a few years, before a submitted
paper is officially published. During this time, few people are aware of the
research that has been done. With public preprint servers, the science is
immediately available and can be openly discussed, analysed, and integrated into
current research. It benefits both science and publishers. Both want the papers
to be well-known and cited, and public preprints make it possible to integrate
research even before publication, improving immediacy.  } \label{fig:map}
\end{figure}

Preprint servers also establish priority in a fair way. Some manuscript will
spend much more time in the review process. Public preprints server offer a much
fairer way to establish intellectual priority By making the manuscript available
when it is ready. Surprisingly, there is perception in biology that public
preprints make it easier to steal ideas, as if scientific ideas only took form
in published material. Mathematicians and physicists have embraced arXiv in part
to establish priority in a fair way\cite{cal12}.

Some of the responses to public preprints are surprisingly since they are,
essentially, the same as exchanging preprints among colleagues. Prepublication
reviews by a small network of colleagues is an important part of the scientific
process. Preprints servers simply offer a way to extend this network of
colleagues to the entire scientific community. It ensures that science is not
constrained by small networks of scientists exchanging ideas. Ginsparg made
arXiv.org in part for democratic reasons: he wanted everyone from graduate
students in small universities to Princeton professors to have access to the
most recent scientific ideas. Ginsparg revolutionary idea was simply to use the
power of the internet for preprints, not just for the end product, so the
process can be open from A to Z, instead of being just open at the end of the
process.

>>>>

Preprints servers such as arXiv are common in mathematics and physics, but
still a minority of papers in ecology and evolution use them. Preprints
servers allow author to make their manuscripts publicly available before, or
in parallel to, submitting them to journals for traditional peer-review. ...
The idea became popular with arXiv, and many physicists start their day with a
look at the new papers in arXiv \cite{gin11}

@@

The review process as a whole is critically over-loaded, because the number of
active scientists increases, because the pressure to publish increases, and
because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  In
the same times, rejection rates are high in most journals (REF), and when the
not invited to submit a revisions, authors are left with the impression that
they must start the whole process all over again. It's thus no surprize that
different initiatives emerged over the last few years, to decrease the time
spent in review. XXX et coll. (REF) called for the recycling and reuse of
peer-reviews: by attaching previous reviews, and detailed replies, to a new
submission, both the editor and the referees can jauge the work done on the
manuscript, and perhaps evaluate it with less prejudice. In a similar way, the
\emph{Peerage of Science} initiative allows authors to seek anonymous pre-
review by their peers. Some journals (LIST?) now accept to publish papers
which received good evaluations, effectively outsourcing the review process. A
widespread use of preprint servers can achieve the same goal of reducing the
time spent in review. By putting a manuscript out there for open comments and
criticisms, the authors will receive valuable feedback, and can improve the
version which will be submitted. With a rich enough community of scientists
depositing preprints, and commenting on them, the process of an open pre-
review can become widespread, and will overall increase the quality of first
submissions.
% Assuming that the quality of the paper is a good prior of its acceptance probability :-)

\begin{figure}[ht!] \centering\includegraphics[width=0.50\textwidth]{map.pdf}
\caption { It can take several months, and even a few years, before a submitted
paper is officially published and citable. During this time, few people are
aware of the research that has been done (typically, close colleagues are
given access to the preprints). With public preprint servers, the science is
immediately available and can be openly discussed, analysed, and integrated
into current research. It benefits both science and publishers. Both want the
papers to be well-known and cited, and public preprints make it possible to
integrate research even before publication, greatly improving immediacy.  }
\label{fig:map}
\end{figure}

Preprint servers also establish priority in a fair way. Some manuscript will
spend much more time in the review process. Public preprints server offer a
much fairer way to establish intellectual priority by making the work
available when done, and even if the exact organisation of the manuscript may
change. Surprisingly, there is perception in biology that public preprints
make it easier to steal ideas, as if scientific ideas only took form in
published material.
% TP This needs more development, I'm not sure I get your point
Mathematicians and physicists have embraced arXiv in part
to establish priority in a fair way\cite{cal12}.

Some of the responses to public preprints are surprising since they are,
essentially, the same as exchanging preprints among colleagues.
% TP Well, no. You trust your colleagues, and you trust that they will not give your
%    MS to anyone!
Prepublication reviews by a small network of colleagues is an important part
of the scientific process, which is attested by the fact that nearly all
published papers acknowledge comments by people not listed as co-authors.
Preprints servers simply offer a way to extend this network of colleagues to
the entire scientific community. It ensures that science is not constrained by
small networks of scientists exchanging ideas. Ginsparg made arXiv.org in part
for democratic reasons: he wanted everyone from graduate students in small
universities to Princeton professors to have access to the most recent
scientific \emph{ideas}.
% TP One important point to make: the MS and the idea are different things.
%    We should focus more on the later...
Ginsparg revolutionary idea was simply to use the power of the internet for
preprints, not just for the end product, so the process can be open from A to
Z, instead of being just open at the end of the process.
% TP Since when is the publishing buisness an open process? :-)
